Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-05-10 analy_eval.tex
[draft] definition and analytic results draft 1

In this subsection, we will demonstrate that the diagrams drawn in the last subsections are all related to the amplitudes between boundary states.

We notice that there is only one apparent length scale in these diagram: in the case of fidelity it is the finite size $L$ for fidelity and $\tau$ for Loschmidt echo. In the absence of the regulators, the conformal invariance can rescale them to $1$ by doing a conformal transformation, thus getting rid of their dependences. Therefore, regulator is necessary in keeping track of the scale dependence in doing the conformal transformation. This is also required by the lattice realization of the systems.

We work in the folding picture, add small semi-circles to the point where the boundary condition changing operator resides. For the fidelity case, the conformal mapping is depicted in Fig.~\ref{fig:fidel-map} 
\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{fig_fidel-map.pdf}
\caption{Mapping from a strip to the upper half plane $w = \frac{L}{\pi} \ln z $. The two black dots represent possible insertion of bcc operators. The dot inside the blue semi-circle is at coordinate $z = 1$, which is the image of point connecting $a$ and $b$ boundaries. The other dot is at $z = 0$, and corresponds to the connection between $a$ and $c$ boundaries at $- \infty$. To evaluate the diagram, we add the outer-semi-circle as the IR cut-off, it can also be regarded as the image of the blue vertical line on the $w$ plane.}
\label{fig:fidel-map}
\end{figure}
If the three boundary conditions $a, b, c$ are all different, then there are two boundary condition changing operators on the real axis. We focus on the one where $a = c$. The two end points of the $\epsilon$ radius semi-circle on the $w$ plane are mapped to
\begin{equation}
\exp( \pm \pi \frac{\epsilon}{ L}  ) \sim 1 \pm \pi \frac{\epsilon}{L} 
\end{equation}
The vertical line at $\text{Re} w = W$ is mapped to $|z| = e^{\pi \frac{W}{L} } \gg 1 $. Since the radius of this larger circle is overwhelming, moving the inner semi-circle on the $z$ plane to the center will not affect the cross ratio to the leading order. The dashed line and solid line are then regarded as two boundary states. The imaginary time evolution is performed in the angular direction and the partition function we are looking for is
\begin{equation}
  Z_{ab} = \langle a | e^{-\pi H } |b \rangle 
\end{equation}

The Loschmidt echo can also be evaluated the same way. We therefore introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulator and then perform a series conformal transformation as shown in Fig.~\ref{fig:H-tau_fold}. In the $\xi$ plane, we end with the same diagram as fidelity. With one more conformal mapping, it is becomes the cylinder partition function between two boundary states.

@@

One should however notice that in performing the conformal transformation, we have introduced shifts in free energy. In fact, the free energy in the boundary state calculation gives a positive exponent, meaning a power law increase of the fidelity and echo, which does not make sense. We inspect the shifts in App.~\ref{app:F_correction}, generally speaking it comes from the Schwartzian term and the regulator.

The amplitude between different boundary states can be computed by the technique presented in App.~\ref{app:lambda_12} and App.~\ref{app:gnd_dn_lambda}, where we set the width of the cylinder to be $\beta$. Adding back the correction in App.~\ref{app:F_correction}, the final result is
\begin{equation}
 - \ln Z_{ab }( \beta ) + \frac{1}{6} \beta 
\end{equation}
where $a,b$ denotes different boundary condition (including the $\lambda$ junction) and $\beta = 2 \ln L$ or  $ 4 \ln \tau$ in the fidelity and echo.

>>>>

In this subsection, we relate the free energy to the amplitudes between boundary states and give analytic results.

We notice that there is only one apparent length scale in these diagrams -- the finite size $L$ for fidelity and imaginary time $\tau$ for the Loschmidt echo. These are the characteristic size of the corner at the tip of the slit. However, without regulators the conformal invariance can rescale both to $1$ by doing a dilation transformation, thus getting rid of their dependence. Therefore, regulators are necessary in keeping track of the scale dependence and also physically sensible considering the lattice realization of the systems.

We thus add small semi-circles around the points where the boundary condition changing operator resides and then do a series of conformal mapping.

For the fidelity case, the regulators as well as conformal mapping are depicted in Fig.~\ref{fig:fidel-map} 
\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{fig_fidel-map.pdf}
\caption{Mapping from a strip to the upper half plane $w = \frac{L}{\pi} \ln z $. The two black dots represent possible insertion of bcc operators. The dot inside the blue semi-circle is at coordinate $z = 1$, which is the image of point connecting $a$ and $b$ boundaries. The other dot is at $z = 0$, and corresponds to the connection between $a$ and $c$ boundaries at $- \infty$. To evaluate the diagram, we add the outer-semi-circle as the IR cut-off, it can also be regarded as the image of the blue vertical line on the $w$ plane.}
\label{fig:fidel-map}
\end{figure}
We assume $a = c$ such that there is only one bcc operator on the real axis enclosed by the regulator. The two end points of the $\epsilon$ radius semi-circle on the $w$ plane are mapped to
\begin{equation}
\exp( \pm \pi \frac{\epsilon}{ L}  ) \sim 1 \pm \pi \frac{\epsilon}{L} 
\end{equation}
The vertical line at $\text{Re} w = W$ (IR regulator) is mapped to $|z| = e^{\pi \frac{W}{L} } \gg 1 $. Since the radius of this larger circle is overwhelming, moving the inner semi-circle on the $z$ plane to the center will not affect the cross ratio to the leading order. The dashed line and solid line can then be regarded as two boundary states, the diagram corresponds to the following partition function
\begin{equation}
  Z_{ab} = \langle a | e^{-\pi H } |b \rangle 
\end{equation}

The Loschmidt echo can be evaluated the same way. Again we introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulator and then perform the conformal transformation shown in Fig.~\ref{fig:H-tau_fold}. In the $\xi$ plane, we end with the same diagram as fidelity. With one more conformal mapping, it is becomes the cylinder partition function between two boundary states.

@@

The results of the general partition function $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and its free energy are evaluated in App.~\ref{app:lambda_12} to the leading order of cylinder width $\beta$. But one can't use these results na\"ively as we have tacitly introduced shifts in doing these conformal transformation. In fact, directly using the free energy given in App.~\ref{app:lambda_12} resulting in a power law increase of Loschmidt echo, which does not agree with the known results. One easy way to see the shift is that free energy is zero when $a,b,c$ are all periodic boundary conditions, hence 
\begin{equation}
\mathcal{F} = - \ln Z_{ab} ( \beta ) + \frac{1}{12} \beta 
\end{equation}
where $\frac{1}{12}\beta$ is the value of $ \ln Z_{ab} ( \beta )$ when $a = b = {\rm P}$. A more careful inspection is performed in App.~\ref{app:F_correction}, where the correction is found to be coming from the Schwartzian and outer circle regulator.

For the process ($c$ is assumed to be the same as $a$)
\begin{equation}
S_i( \theta_1 ) \rightarrow S_j( \theta_2 ) 
\end{equation}
the free energy is
\begin{equation}
\mathcal{F}( \beta )  = 
\left\lbrace
\begin{aligned}
  &\frac{1}{2}(-|x| + x^2 )\beta  \quad &i = j \\
  &\frac{1}{16}\beta   \quad &i \ne j   \\
\end{aligned} \right. \quad x = \frac{\theta_2 - \theta_1}{\pi} 
\end{equation}
We can then read off the fidelity and Loschmidt echo power law decay exponent with the identification $\beta = 2 \ln L$ and $ 4 \ln \tau$.

### 2017-05-10 def_fidel_echo.tex
[draft] definition and analytic results draft 1

Bipartite fidelity is the overlap of the groundstates of two Hamiltonians. In the path integral language, the groundstates can be produced by imaginary time evolution. If we take the horizontal axis as the Euclidean time, the fidelity can be diagrammatically represented as in Fig.~\ref{fig:fidel}. Treating it as a partition function, we analyze its finite size dependence on the total chain size $L$. The logarithmic fidelity should then follow the general discussion of Cardy and Peschel\cite{cardy_finite-size_1988} of the finite size dependence of free energy and give a term proportional to $\ln L$
\begin{equation}
\mathcal{F} = - \ln \langle \phi_1 |\phi_2 \rangle^2 = - 2 \ln Z  \sim  \ln L 
\end{equation}
The proportionality constant is the exponent characterizing the interface.

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{fig_fidel.pdf}
\caption{Fidelity of connecting two CFTs. The horizontal axis the imaginary time. Evolution on the two infinitely extended side produces the groundstate of the disconnected and connected chain Hamiltonians. The right diagram is the result of folding the lower part of the diagram up, so that all the boundary are now boundary states.}
\label{fig:fidel}
\end{figure}

@@

The Loschmidt echo is defined to be defined as the overlap of the ground state and the quenched states, 
\begin{equation}
\mathcal{L} = |\langle \phi_{\rm gnd}  | e^{-i Ht } | \phi_{\rm gnd} \rangle|^2
\end{equation}
We have drawn the path integral definition of this quantity in Fig.~\ref{fig:cut-and-join}; for convenience of the latter conformal mapping, we turn the diagram by a right angle and take the horizontal axis as time. The slits represents disconnected boundary conditions like Dirichlet and Neumann, the dashed line represent partially transmitting boundary condition parameterized by $\lambda$. We may as well fold the lower half plane up and everything on the real axis should be regarded as boundary states. Again by Cardy and Peschel\cite{cardy_finite-size_1988}, the logarithm of the Loschmidt echo is the free energy and should have logarithmic dependence on the characterizing length scale in the problem. In other words
\begin{equation}
\mathcal{L} = - \ln |\langle \phi_{\rm gnd}  | e^{-i Ht } | \phi_{\rm gnd} \rangle|^2 \propto \ln \tau 
\end{equation}

>>>>

In this section, we define the fidelity and Loschmidt echo and present their corresponding spacetime path integral diagrams. It will then be evident that these quantities are just the free energy of Boson with conformal interfaces (or boundaries).

Fidelity is the square of the overlap of the groundstates of two Hamiltonians, 
\begin{equation}
{\rm fidelity} = |\langle \psi_1 |\psi_2  \rangle |^2 
\end{equation}
For the systems we considered, $|\psi_1 \rangle$ is the groundstate of the two disconnected chain (of equal length, hence "bipartite") and $|\psi_2\rangle$ is that of the connected chain with conformal defect. Both of them can be produced by the imaginary time evolution. Taking the horizontal axis as imaginary time, the fidelity can be diagrammatically represented as in Fig.~\ref{fig:fidel}, where the slits represents the disconnected boundary condition, such as Dirichlet(D) and Neumann(N), and the dashed line represents the conformal interface parameterized by $\lambda$. The logarithmic fidelity is then (twice) the free energy of this diagram
\begin{equation}
\mathcal{F}( {\rm fidelity} )  = - \ln \langle \psi_1 |\psi_2 \rangle^2 = - 2 \ln Z
\end{equation}

\begin{figure}[h]
\centering
\includegraphics[width=0.8\textwidth]{fig_fidel.pdf}
\caption{Fidelity of connecting two CFTs. The horizontal axis the imaginary time. Evolution on the two infinitely extended side produces the groundstate of the disconnected and connected chain Hamiltonians. The right diagram is the result of folding the lower part of the diagram up, so that all the boundary are now boundary states.}
\label{fig:fidel}
\end{figure}

@@

The Loschmidt echo is also the (square of the) overlap of two wavefunctions. One of the them the groundstate of the disconnected chain and the other is groundstate evolved by the connected chain Hamiltonian
\begin{equation}
\mathcal{L} = |\langle \psi_{\rm gnd}  | e^{-i H t } | \psi_{\rm gnd} \rangle|^2
\end{equation}
The path integral definition of this quantity would be similar to Fig.~\ref{fig:cut-and-join}, but to be consistent with the fidelity diagram, we take the horizontal axis as imaginary time and present it in Fig.~{\color{red} TODO}. Viewing the diagram as a partition function subject to the switching of boundary conditions, the logarithmic Loschmidt is also the associated the free energy.

If the interface is completely transparent, i.e. at the special point of $\lambda = 1$, the tip of the slits can be regarded as corner singularities. According to Cardy and Peschel\cite{cardy_finite-size_1988}, they will contribute to a term that is logarithmic of the corner's characteristic size, which is $\ln L$ in fidelity and $\ln \tau$ in Loschmidt echo. One would expect the fidelity and echo to have power law decay patter with respective to these scales in the long wavelength limit. In fact, such kind of computation has been done in Ref.~\onlinecite{stephan_logarithmic_2013,stephan_local_2011,vasseur_universal_2014,vasseur_crossover_2013,kennes_universal_2014} using either the Cardy-Peschel formula or Wald identity integration. If the slits boundary conditions are taken to be Dirichlet, we have the universal behavior for the leading term \cite{stephan_logarithmic_2013,stephan_local_2011}
\begin{equation}
\label{eq:full-pass}
\mathcal{F}({\rm fidelity}) =  \frac{c}{8} \ln L \qquad \mathcal{F}( {\rm echo} )  = \frac{c}{4} \ln \tau 
\end{equation}

The tip of the slit is no longer a twist field with presence of the conformal interface. Its nature is clearer in the folding picture shown in Fig.~\ref{fig:fidel} and {\color{red} TODO} where the lower half plane is flipped up on top of the upper half plane on both fidelity and echo diagram. From the boundary conformal field theory point of view, the change of boundary condition can be regarded as insertion of primary fields called boundary condition changing(bcc) operator. These diagrams then becomes the one and two point functions of the bcc operators and the free energy logarithmic term extracts their scaling dimensions.
